Cradles of the first stars: self-shielding, halo masses, and multiplicity

### 2019-10-22 paper.tex
Fixing small error

% MNRAS is set in Times font. If you don't have this installed (most LaTeX
% installations will be fine) or prefer the old Computer Modern fonts, comment
% out the following line
\usepackage{newtxtext,newtxmath}
% Depending on your LaTeX fonts installation, you might get better results with 
% one of these:
%\usepackage{mathptmx}
%\usepackage{txfonts}

@@

The first generation of stars transformed a cold and dark universe 
by illuminating and enriching up their neighborhoods with radiation
and heavy elements. The formation of these first stars is a crucial step in the cosmological evolution of the universe because the metals and feedback they deliver to their local environments are necessary for further star production and chemical enrichment. Without these initial stars, heavier metals would not have been produced, and a different universe would be observed than what is observed today. These stars are, by definition, metal-free (Population III; Pop III) and are \textbf{traditionally} thought to be generally massive \citep{ABN02, Bromm02_P3, Turk09, Hosokawa11, Hosokawa16, Hirano15}\textbf{, although more recent work has shown that lower mass ($M < 1 M_{\odot}$) Pop III stars can be formed \citep{Greif11_P3Cluster, Clark11_Frag, Stacy11}} A substantial fraction of these stars will generate prodigious amounts of ionizing photons and will end their lives in some form of a supernova \citep[e.g.][]{Schaerer02, Heger02}. The supernova will spread the enriched guts of the Pop III star out across its local environment, providing the area with elements the universe has not yet seen.

>>>>

% MNRAS is set in Times font. If you don't have this installed (most LaTeX
% installations will be fine) or prefer the old Computer Modern fonts, comment
% out the following line
%\usepackage{newtxtext,newtxmath}
% Depending on your LaTeX fonts installation, you might get better results with 
% one of these:
%\usepackage{mathptmx}
%\usepackage{txfonts}

@@

The first generation of stars transformed a cold and dark universe 
by illuminating and enriching up their neighborhoods with radiation
and heavy elements. The formation of these first stars is a crucial step in the cosmological evolution of the universe because the metals and feedback they deliver to their local environments are necessary for further star production and chemical enrichment. Without these initial stars, heavier metals would not have been produced, and a different universe would be observed than what is observed today. These stars are, by definition, metal-free (Population III; Pop III) and are \textbf{traditionally} thought to be generally massive \citep{ABN02, Bromm02_P3, Turk09, Hosokawa11, Hosokawa16, Hirano15}\textbf{, although more recent work has shown that lower mass ($M < 1 M_{\odot}$) Pop III stars can be formed \citep{Greif11_P3Cluster, Clark11_Frag, Stacy11}.} A substantial fraction of these stars will generate prodigious amounts of ionizing photons and will end their lives in some form of a supernova \citep[e.g.][]{Schaerer02, Heger02}. The supernova will spread the enriched guts of the Pop III star out across its local environment, providing the area with elements the universe has not yet seen.
